VM-Centric Deduplication with Fault Isolation for Snapshot Backup in the Cloud

### 2014-01-28 snapshot_system/paper_intro.tex

@@

In this paper {\em we explore a method for deduplicating VM snapshots in
converged architecture IaaS systems that strikes a balance between fault
isolation and storage efficiency}.  The main contribution of this work is to
evaluate the impact of sharing only ``popular'' data blocks 
(through deduplication and limited replication)
across 
virtual machines while using localized deduplication within each VM
to achieve both storage savings and fault isolation.
%, and to propose a VM-centric approach that localizes
%deduplication as much as possible and restricts global deduplication only to a
%limited set of most popular blocks.  
%In our method, local deduplication uses
%similarity-guided elimination to improve the deduplication coverage.  
Since
the file system block size is normally bigger than the average data chunk size
used for deduplication, 
our approach uses a deduplication data chunk size that is smaller than a
single file block and
packages data chunks from the same VM into a file
system block as much as possible to improve fault isolation.  Deduplicating
data locally within a VM also reduces the need to maintain a global index of
chunks that are shared among VMs, thereby increasing the scaling efficiency of
the snapshot system.  The cost associated with localization, however, is in 
the lost
storage efficiency that cross-VM deduplication makes possible.  To recover
some of this efficiency we allow a small number of the most popular data
blocks to be deduplicated (and then replicated) across VMs.

This work explores the storage and
performance efficiencies that such a {\em VM-centric} 
combination of local and global
techniques can achieve.  We term it VM-centric because the deduplication
algorithm considers VM boundaries in making its decisions as opposed to
treating all blocks as being equivalent within the storage system.
We detail the storage, performance,
and fault isolation properties
of our method and verify these properties empirically using a prototype
system that we have developed to run as a co-located back-up service in
converged IaaS cloud enviornments.

>>>>

Without deduplication,
the cloud typically offloads backup workload from production 
server hosts to dedicated backup proxy servers (e.g. EMC Data Domain) or
backup services (e.g. Amazon S3). This approach simplifies the cluster 
architecture and 
avoids potential performance degredation to production applications when 
backups are in progress.
However, sending out pre-deduplication backup data wastes huge amount
of network bandwidth that would otherwise be available to user VMs. 
Even when the storage system implements deduplication internally
such dedicated backup storage is either difficult to scale out
(which can comprise the overall scalability of the converged architecture) 
or it must forego global deduplication in order to gain scalability 
(which increases backup cost).

In this paper we propose a backup service for converged cloud architectures
that is co-located with user VMs, sharing the cloud computer, network, and
storage resource swith them.
We describe methodologies to address the following challenges: 
\begin{itemize}
\item good global deduplication efficiency using a distributed implementation
that limits its resource usage, 
\item augmented fault isolation for the sharing of deduplicated data,
given that node failures in converged architecture are the norm rather than
exception, and
\item efficient garbage collection so that users stop incurring 
storage charges immediately after snapshot deletion.
\end{itemize}

% low-cost VM-centric snapshot backup approach that is collocated within 
% the existing converged storage architecture. Our solution leverages the scalability of the underlying
% distributed file system and provides global data deduplication in a resource friendly manner.

%For example, the Aliyun cloud, which is  the largest cloud service provider by Alibaba in China, 
%automatically conducts  the backup of virtual disk images to all active users every day.
%The cost of supporting a large number of concurrent backup streams is high
%because of the huge storage demand and the use of deduplication

@@

The main technical approach of our work focuses on
sharing only ``popular'' data blocks 
(through deduplication and limited replication)
across 
virtual machines while using localized deduplication within each VM
to achieve both storage savings and fault isolation.
%, and to propose a VM-centric approach that localizes
%deduplication as much as possible and restricts global deduplication only to a
%limited set of most popular blocks.  
%In our method, local deduplication uses
%similarity-guided elimination to improve the deduplication coverage.  
Since
the file system block size is normally bigger than the average data chunk size
used for deduplication, 
our approach uses a deduplication data chunk size that is smaller than a
single file block and
packages data chunks from the same VM into a file
system block as much as possible to improve fault isolation.  Deduplicating
data locally within a VM also reduces the need to maintain a global index of
chunks that are shared among VMs, thereby increasing the scaling efficiency of
the snapshot system.  The cost associated with localization, however, is in 
the lost
storage efficiency that cross-VM deduplication makes possible.  To recover
some of this efficiency we allow a small number of the most popular data
blocks to be deduplicated (and then replicated) across VMs.

This paper explores the storage and
performance efficiencies that such a {\em VM-centric} 
combination of local and global
techniques can achieve.  We term it VM-centric because the deduplication
algorithm considers VM boundaries in making its decisions as opposed to
treating all blocks as being equivalent within the storage system.
We detail the storage, performance,
and fault isolation properties
of our method and verify these properties empirically using a prototype
system that we have developed to run as a co-located back-up service in
converged IaaS cloud enviornments.
